### 2014-09-30 paper/include/introduction.tex
more reorganization

\section{Introduction}
\label{sec:int}
Why is it important to reduce the refreshes?
Briefly mention the methods.

>>>>

\section{Introduction}
\label{sec:int}
\textbf{Whats the problem?}
energy is an inc. system design constraint

\textbf{Why is it important?}
Main mem consumes a groving portion of system power and this will continue to increase (details \& refs in background)

Mention 3D stacked DRAM: higher tempratures, which gives a higher refresh rate that also increases temratures.

Most main memories include dramtwo ssources of powerconsumption in DRAM static/dynamic (blahah/driving data)
static leakage

\textbf{What is the shape of the solution?}
DRAM refresh ops account for a groing portion of dynamic power, yet they perform no usefiul accesses (from cpu perspective)

\textbf{Why will it work? (dont go into detail, this is a survey paper)}
Finding ways to reduce power spent on frefresh is a straightfroward way to mitigate DRAM power

Briefly mention the methods to lower the refresh rate.
